Many compilers have an option for warning about unused variables.
Even though such warnings can be disabled altogether,
it is a good idea to enable them by default, and selectively suppress them
for certain variables by adding a dummy expression with a \tt{Void} cast;
this is a common trick for suppressing warnings about unused parameters.

The only downside of the approach is that expression statements cannot
be used outside functions (or any kind of statement for that matter),
so if there are unused ``private'' variables (internal linkage)
created for future use, then this approach requires an additional
function where we can add dummy expressions that use such variables.

C\_ offers an alternative with \idx{spares_},
which is syntactically a declaration, so it can also occur outside functions.

\head{Syntax}

\tt{spares_ (} \it{identifier-list} \tt{)}

\pagebreak

\head{Constraint}

\it{identifier-list} shall be a comma separated list of identifiers,
and each identifier shall refer to a variable or a function.
At least one identifier shall be provided and no identifier shall be repeated;
an identifier that has already been used in a \tt{spares_} declaration shall
not be reused in a subsequent \tt{spares_} declaration within the same scope.

\head{Semantics}

\tt{spares_} declares that variables or functions
specified in \it{identifier-list} are potentially unused;
the list should not end with a trailing comma, as implementations are
not required to support it, and can be treated as a syntax error.

\note C23 adds the standard attribute \tt{maybe_unused}
that should be preferred if supported by the compiler.
