The defer family allows statements to be postponed, which are executed after
reaching the end of the innermost block that is lexically closed with \tt{refed}.
This feature is useful for registering cleanup or release of resources.

\example Consider a function that needs $n$ resources for some task;
if a resource is not available, then the acquired resources must be released.
With three resources, we can express this requirement with the following code.

\enlargethispage*{\baselineskip}

\code{Statements/Defer/quadratic.c_}

The crucial observation is that resource $i$ has
to be released if another resource is available.
A call to \tt{release} lexically occurs  $i$ times for the $i^{th}$ resource,
so for $n$ resources there will be $n * (n + 1) / 2$
instances of \tt{release} calls, even though at most $n$ such
calls will actually be made (one for each acquired resource).
This bloats the executable as code size grows at a
quadratic rate in terms of the number of resources.
\tt{defer_} offers a more elegant approach by postponing the release of acquired
resources; deferred statements are executed in reverse order of registration.

\note Before presenting a cleaner alternative with \tt{defer_},
we shall take another look at the earlier code,
and observe the use of brace-enclosed nested blocks: the intent is to make
a released resource unavailable for any subsequent use, which is done by
making the pointer variable go out of scope just after calling \tt{release}.
Some programmers advocate setting it to \tt{NULL},
so that defensive null pointer checks can catch an invalid use;
however, that means the variable has to be modifiable,
which opens up the possibility of unintended mutations due to bugs.

We prefer to follow the previous chapter's advice on enforcing
immutability as much as possible, so we rely on scoping rules instead:
every resource is associated with its own lexical scope that starts with
the resource is acquired, and ends when the resource is released; this
ensures that each pointer variable is no longer accessible once its use is over.
Plain nested scopes can prove beneficial in the
long run for functions that manage several resources.
We consider this practice as a part of structured
programming that has also been followed in later chapters.

\subsection{\idX{defer_}* and \idX{refed}*}
\input{Statements/Defer/defer_ and refed}

\enlargethispage*{\baselineskip}
\pagebreak

\subsection{\idX{deferrable}* and \idX{start}*}
\input{Statements/Defer/deferrable and start}

\subsection{\idX{return_}* and \idX{yield}*}
\input{Statements/Defer/return_ and yield}

\subsection{\idx{DEFER_MAX}}
\input Statements/Defer/DEFER_MAX
