\def\Subsection#1{\subsection{\idx{#1}}\input{Interfaces/Abstract type/#1}}

\tt{Abstract} type extends the \tt{Object} class, and by virtue of inheritance,
\idx{struct Abstract} contains a member \idxy{struct Abstract}{base}
defined as a singleton array whose element type is \tt{Object_}.
\tt{Abstract_} is a synonym for \tt{struct Abstract},
while \tt{Abstract} is its non-modifiable counterpart.
The member \idxy{struct Abstract}{type} is an alias for \tt{base->type},
which is initialized by the \tt{Abstract} constructor to point to the \tt{Type}
structure of \tt{Abstract}, containing pointers to overridden procedures.
\tt{Abstract} structure also contains a pointer member that
can be accessed with three names having different types:

\begin{itemize}

\item The name \idxy{struct Abstract}{concrete}  is declared
as pointer to \tt{Void},  referring to a non-modifable object.

\item The name \idxy{struct Abstract}{concrete_} is declared
as pointer to \tt{Void_}, referring to a modifiable object.

\item The name \idxy{struct Abstract}{_concrete} is a pointer to an
untagged union with two members, both aliased to the same pointer:
\idxyz{struct Abstract}{_concrete}{type}  is a pointer to \tt{struct Type}, and
\idxyz{struct Abstract}{_concrete}{typex} is a pointer to an extended \tt{Type},
with \tt{Typex_(Abstract)} being a synonym for the pointer type
(\tt{Type} extension using interfaces is documented in a later section).

\end{itemize}

When an interface is instantiated with \tt{Type} of a concrete class,
the above three names alias to the same member, pointing
to an instance of the class that concretizes the interface.
The member \tt{type} (or \tt{base->type}) provides the abstract lineage,
while \tt{_concrete->type} points to \tt{Type} of the
implementing class, providing the concrete lineage.

The macros \idx{Abstract_EXTENDS} and \idx{SELF_IMPLEMENTS_Abstract}
are reserved for implementations of C\_.

\note The generic pointer type aliases are used to avoid
boilerplate casts during assignments and invocations.

\Subsection{concrete_}
