\def\Section#1{\section{#1}\input{Classes/#1}}

A class is used to associate well-defined functionalities with data objects:
the behavior is described by protocols and implemented by procedures.
A class defines a concrete data type, which means that the names
and types of data members are declared along with the class type,
and this information can be used to directly modify an attribute.
Every class is associated with a set of methods, which provide a controlled
mechanism for accessing and updating the state of an instance; however,
concrete data types can be modified directly as their member details are known.

Each value of a class type is called an ``instance''
of that class: it is (pointer to) a structure that
contains the member attributes of that class type.
Every instance has an implicit attribute that specifies the dynamic
type of that object: it is nothing but a pointer to a non-modifiable
structure of function pointers, which is same for all instances
of the same class, but different across multiple classes.
Additionally, the type pointer also creates a static
relationship between a class and its base type, establishing
a type lineage all the way to the root ancestor \tt{Object}.

Influenced by existing object-oriented languages, instances are typically
manipulated via references, guaranteeing a small constant overhead (independent
of structure size) when passed as function arguments or copied as return value.
Another existing convention we shall follow is to start the name of an
object-oriented type with an uppercase letter, and have at least one lowercase
letter in the name (to differentiate them from object-like macros usually named
entirely in uppercase); this practice is consistent with the notion of classes
and interfaces being user defined data types, hence we follow the same naming
scheme as for C\_ type synonyms (a trailing underscore means modifiable).

\note We shall use the term ``object-oriented types''
for collectively referring to both classes and interfaces.

\section{\type{Type} structure}
\input{Classes/Type structure}

\section{\type{Object} class structure}
\input{Classes/Object class structure}

\Section{Obtaining the type}

\Section{Type inheritance}

\Section{Type relationships}

\section{\tt{Type} methods}
\input{Classes/Type methods}

\section{\tt{Object} class procedures}
\input{Classes/Object class procedures}

\Section{Creating a class}

\Section{Implementing procedures}

\Section{More examples}
